### 2019-10-16 ch3_dynbenchmark/content.tex
update

		Dependencies & (1) Dependencies are clearly stated in the tutorial or in the code (2) Dependencies are automatically installed & \cite{taschuk_tensimplerules_2017,wickham_packagesorganizetest_2015,artaza_top10metrics_2016,karimzadeh_topconsiderationscreating_}\\*

@@

		Dummy proofing & Package contains dummy proofing, i.e. testing whether the parameters and data supplied by the user make sense and are useful & \cite{lee_rpackagespackagedevelopment_2017,karimzadeh_topconsiderationscreating_}\\

@@

		Tutorial & (1) A tutorial or vignette is available (2) The tutorial has example results (3) The tutorial has real example data (4) The tutorial showcases the method on several datasets (1=0, 2=0.5, >2=1) & \cite{wickham_packagesorganizetest_2015,silva_generalguidelinesbiomedical_2017,jimenez_foursimplerecommendations_2017,karimzadeh_topconsiderationscreating_,boulesteix_tensimplerules_2015}\\*

		Function documentation & (1) The purpose and usage of functions/commands is documented (2) The parameters of functions/commands are documented (3) The output of functions/commands is documented & \cite{wilson_bestpracticesscientific_2014,taschuk_tensimplerules_2017,wickham_packagesorganizetest_2015,silva_generalguidelinesbiomedical_2017,karimzadeh_topconsiderationscreating_}\\*

		Inline documentation & Inline documentation is present in the code & \cite{wilson_bestpracticesscientific_2014,taschuk_tensimplerules_2017,wickham_packagesorganizetest_2015,silva_generalguidelinesbiomedical_2017,karimzadeh_topconsiderationscreating_}\\*

@@

		Peer review & The paper is published in a peer-reviewed journal & \cite{karimzadeh_topconsiderationscreating_,gannon_essentialrolepeer_2001,baldwin_refereeswetrust_2017}\\*

@@

		Evaluation of robustness & The paper assessed method robustness (to eg. noise, subsampling, parameter changes, stability) in one (0.5) or several (1) ways & \cite{karimzadeh_topconsiderationscreating_,aniba_issuesbioinformaticsbenchmarking_2010,boulesteix_tensimplerules_2015,jelizarow_overoptimismbioinformaticsillustration_2010}\\

>>>>

		Dependencies & (1) Dependencies are clearly stated in the tutorial or in the code (2) Dependencies are automatically installed & \cite{taschuk_tensimplerules_2017,wickham_packagesorganizetest_2015,artaza_top10metrics_2016,karimzadeh_topconsiderationscreating_2018}\\*

@@

		Dummy proofing & Package contains dummy proofing, i.e. testing whether the parameters and data supplied by the user make sense and are useful & \cite{lee_rpackagespackagedevelopment_2017,karimzadeh_topconsiderationscreating_2018}\\

@@

		Tutorial & (1) A tutorial or vignette is available (2) The tutorial has example results (3) The tutorial has real example data (4) The tutorial showcases the method on several datasets (1=0, 2=0.5, >2=1) & \cite{wickham_packagesorganizetest_2015,silva_generalguidelinesbiomedical_2017,jimenez_foursimplerecommendations_2017,karimzadeh_topconsiderationscreating_2018,boulesteix_tensimplerules_2015}\\*

		Function documentation & (1) The purpose and usage of functions/commands is documented (2) The parameters of functions/commands are documented (3) The output of functions/commands is documented & \cite{wilson_bestpracticesscientific_2014,taschuk_tensimplerules_2017,wickham_packagesorganizetest_2015,silva_generalguidelinesbiomedical_2017,karimzadeh_topconsiderationscreating_2018}\\*

		Inline documentation & Inline documentation is present in the code & \cite{wilson_bestpracticesscientific_2014,taschuk_tensimplerules_2017,wickham_packagesorganizetest_2015,silva_generalguidelinesbiomedical_2017,karimzadeh_topconsiderationscreating_2018}\\*

@@

		Peer review & The paper is published in a peer-reviewed journal & \cite{karimzadeh_topconsiderationscreating_2018,gannon_essentialrolepeer_2001,baldwin_refereeswetrust_2017}\\*

@@

		Evaluation of robustness & The paper assessed method robustness (to eg. noise, subsampling, parameter changes, stability) in one (0.5) or several (1) ways & \cite{karimzadeh_topconsiderationscreating_2018,aniba_issuesbioinformaticsbenchmarking_2010,boulesteix_tensimplerules_2015,jelizarow_overoptimismbioinformaticsillustration_2010}\\
